Datasamling

### 2022-01-13 Data/Data_Henting_Backup.Rmd
Lagd datasett

@@

```{r}
har_bos <- har_bos %>% 
  mutate(
    Ullensvang = `1231_Ullensvang (1977-2019)` + `4618_Ullensvang`,
    Totalt = `1228_Odda (1913-2019)` + Ullensvang) %>% 
  select(NACE2007, Kjonn, Alder, ContentsCode, aar, Totalt)
```

@@

#oppgave 3
write_csv(hld_bos_LQ, file="hld_bos_LQ.csv")
write_csv(sun_bos_LQ, file= "sun_bos_LQ.csv")
#oppgave 4
write_csv(Pendling, file = "Pendling.csv")
write_csv(hgl_Pendling, file = "hgl_Pendling.csv")
write_csv(sun_Pendling, file = "sun_Pendling.csv")
```

>>>>

```{r}
har_bos <- har_bos %>% 
  mutate(
    Ullensvang = `1231_Ullensvang (1977-2019)` + `4618_Ullensvang`,
    Totalt = `1228_Odda (1913-2019)` + Ullensvang) %>% 
  select(NACE2007, Kjonn, Alder, ContentsCode, aar, `1228_Odda (1913-2019)`, Ullensvang)
```

```{r}
har_bos_LQ <- har_bos

names(har_bos_LQ)[[6]] <- "Odda(-2019)"
names(har_bos_LQ)[[7]] <- "Ullensvang"

har_bos_LQ <- har_bos_LQ %>% 
  mutate(
    Kjonn = fct_recode(Kjonn,
                     "Begge Kjønn" = "0"))

har_bos_LQ <- har_bos_LQ %>% 
  mutate(
    NACE2007 = fct_recode(NACE2007,
                     "Alle Næringer" = "00-99",
                       "Primærnæring" = "01-03",
                       "Industri" = "10-33",
                       "Undervisning" = "85",
                       "Helsetjenester" = "86-88"))

har_bos_LQ <- har_bos_LQ %>%
  filter(NACE2007 %in% c("Alle Næringer", "Primærnæring", "Industri", "Undervisning", "Helsetjenester")) %>% 
  pivot_wider(
    names_from = NACE2007,
    values_from = c("Odda(-2019)", "Ullensvang")) %>% 
  mutate(
    Totalt_Reg_Næringer = `Odda(-2019)_Alle Næringer` + `Ullensvang_Alle Næringer`,

    Totalt_Reg_Industri = `Odda(-2019)_Industri` + Ullensvang_Industri,

    Totalt_Reg_Primærnæring = `Odda(-2019)_Primærnæring` + `Ullensvang_Primærnæring`,

    Totalt_Reg_Undervisning = `Odda(-2019)_Undervisning` + `Ullensvang_Undervisning`,

    Totalt_Reg_Helsetjenester = `Odda(-2019)_Helsetjenester` + `Ullensvang_Helsetjenester`)
```

@@

@@

#oppgave 3
write_csv(hld_bos_LQ, file="hld_bos_LQ.csv")
write_csv(sun_bos_LQ, file="sun_bos_LQ.csv")
write_csv(har_bos_LQ, file="har_bos_LQ.csv")
#oppgave 4
write_csv(Pendling, file = "Pendling.csv")
write_csv(hgl_Pendling, file = "hgl_Pendling.csv")
write_csv(sun_Pendling, file = "sun_Pendling.csv")
```
